---
title: "rQuoting"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced rQuoting}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Start by loading <span style = "font-family: 'orbitron'"> rQuote </span>.

```{r setup, message = FALSE, warning = FALSE}
library(rQuote)
```

```{r, echo = FALSE}
set.seed(268)
```

Running `rQuote()` without changing any of the default arguments, will print a 'science' tagged quote on your console as well as on a pop-up graphics device:

```{r}
rQuote()
```

<img src = "../niels_bohr.png">

You can change the theme of the pop-up graphics device by specifying `theme = dark`

```{r, echo = FALSE}
set.seed(268)
```

```{r}
rQuote(theme = 'dark')
```

<img src = "../niels_bohr_dark.png">

To get a quote from a tag different than 'science', simply change the tag argument. For example you can get a quote about statistics by specifying `tag = 'statistics'`

```{r, echo = FALSE}
set.seed(1)
```

```{r}
rQuote(tag = 'statistics')
```

<img src = "../mark_twain_statistics.png">

For more information on what types of tags are possible see the \textbf{Details} section of the help page: [`rQuote()`](../reference/rQuote.html).

To quote yourself, you can use function [`rQuoteMe()`](../reference/rQuoteMe.html). Here is an example of me quoting myself using the dark theme:

```{r}
rQuoteMe(quote = 'There are moments in life when randomly quoting the words of someone else, is better than not saying anything. Just keep in mind that these moments are very rare.', 
         author = 'Greg Papageorgiou', 
         theme = 'dark')
```

<img src = "../Greg_quote.png">
